Staged Abstract Interpreters

### 2018-11-12 paper/70_related.tex
related work

Abstract interpretation \cite{DBLP:conf/popl/CousotC77}.

Abstracting Definitional Interpreter \cite{DBLP:journals/pacmpl/DaraisLNH17}.

@@

\textbf{Modular Static Analysis}.

Cousot \& Cousot \cite{DBLP:conf/cc/CousotC02}, 
Compositional shape analysis \cite{DBLP:conf/popl/CalcagnoDOY09}

>>>>

Abstract interpretation was proposed as a semantic-based approach to construct sound static analysis by approximation \cite{DBLP:conf/popl/CousotC77}.
As semantic artifacts, the Abstracting Abstract Machines (AAM) \cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10}
approach shows that abstract interpreters can be derived systematically from concrete semantic artifacts.
The big-step abstract interpreters we presented in this paper are also inspired by the AAM framework,
which are later adopted for big-step abstract interpreters \cite{DBLP:journals/pacmpl/DaraisLNH17, Wei:2018:RAA:3243631.3236800}.

@@

\citet{DBLP:conf/cc/CousotC02} also proposed an abstract interpretation framework for modular analysis.
\citet{DBLP:conf/popl/CalcagnoDOY09} developed compositional shape analysis by using bi-abduction.
